Variation in use of East Asian Late Paleolithic weapons: A study of tip cross-sectional area of stemmed points from Korea

### 2022-10-27 analysis/paper/paper.qmd
added colors to the gis plot
updated shapefiles for new eco-regions, and tried to use the previous codes to create plots

ggplot() +
  geom_sf(data = veg, fill=c("#CCCCCC", "#FFFFFF", "#999999", "#666666")) + #add color for vegetation polygons
  geom_sf(data = pts)

@@

summary(aov(min_tcsa ~ as.factor(Vegetation), points_in_veg_zones))
```

>>>>

ggplot() +
  geom_sf(data = veg, aes(fill = veg$Vegetation)) + #add color for vegetation polygons
  geom_sf(data = pts, aes(color = pts$min_tcsa)) +
  theme_minimal()

# fill=c("#CCCCCC", "#FFFFFF", "#999999", "#666666")

@@

summary(aov(min_tcsa ~ as.factor(Vegetation), points_in_veg_zones))

############ explore tcsa with MODERN eco_regions #####

veg_all <- read_sf(here("analysis/data/gis_data/eco_region.shp"))

veg_all <- st_transform(veg_all, crs = st_crs(4162))

ggplot() +
  geom_sf(data = veg_all) +
  coord_sf()

pts_all <- st_as_sf(korean_archaeological_site_locations_tcsa,
                coords = c(   "long_dd.y", "lat_dd.y"),
                crs = st_crs(veg_all))
ggplot() +
  geom_sf(data = pts_all)

points_in_veg_zones_all <- 
st_join(veg_all, 
        pts_all, 
        join = st_contains)

ggplot() +
  geom_sf(data = veg_all, aes(fill = veg_all$ecoregion)) + #add color for vegetation polygons
  geom_sf(data = pts_all, aes(color = pts_all$min_tcsa)) +
  theme_minimal()

ggplot(points_in_veg_zones_all) +
  aes(ecoregion,
      min_tcsa) +
  geom_boxplot() +
  geom_quasirandom()

summary(aov(min_tcsa ~ as.factor(ecoregion), points_in_veg_zones_all))
